Using the UK Biobank as a global reference of worldwide populations: application to measuring ancestry diversity from GWAS summary statistics

### 2021-11-09 paper-ancestry-prop.tex
save

% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Wed Oct 27 13:40:20 2021
\begin{table}[htb]
	\centering
	\begin{tabular}{|l|c||c|c|c|c|c||c|c|c||c|c|c|c|c|c|c|c|}
		\hline
		Population & N & BBJ & FinnGen & Per\'u & Qatar & Africa & UKBB & GERA & PAGE & BrCa & PrCa & CAD & body fat & covid & eczema & epilepsy & urate \\ 
		\hline
		Africa (West) & 735 &  &  &  &  & 36.7 & 1.4 & 1.9 & 26.4 & 0.2 & 0.2 & 2.4 & 1 & 4 & 0.3 & 0.6 & 3.6 \\ 
		Africa (South) & 449 &  &  &  &  & 63.3 & 0.3 & 0.4 & 6.8 &  & 0.1 & 0.9 & 1.1 & 1.2 & 0.1 &  & 4 \\ 
		Africa (East) & 276 &  &  &  & 11.4 &  &  &  & 0.2 &  &  &  & 0.2 & 0.1 &  &  & 1.4 \\ 
		Africa (North) & 268 &  &  &  & 22.1 &  &  & 0.4 & 2 &  &  &  &  &  &  & 0.3 &  \\ 
		\hline
		Middle East & 523 &  &  &  & 63.5 &  & 1.3 & 3.4 & 0.5 & 2 & 2.2 & 5.2 & 2.9 & 1.5 & 1.6 & 3.2 & 2.8 \\ 
		\hline
		Ashkenazi & 1975 &  &  &  & 1.9 &  & 1.4 & 6 & 0.9 & 1.3 & 3.3 & 2.2 & 2.3 & 1.3 & 2 & 3.6 & 1.5 \\ 
		Europe (North East) & 320 &  & 8.9 &  &  &  & 3.8 & 7.7 & 0.7 & 9.6 & 10 & 10 & 11 & 11.7 & 10.1 & 8.9 & 7.5 \\ 
		Finland & 143 (+ 99) &  & 85.2 &  &  &  & 2.7 & 3.5 & 0.7 & 11.9 & 14.8 & 8.2 & 10.5 & 15.4 & 13.1 & 7.1 & 4.3 \\ 
		British-Irish Isles & 4000 &  & 5.1 &  &  &  & 79.1 & 53 & 8.9 & 59.8 & 56.1 & 46.6 & 49.2 & 54.8 & 61.7 & 62 & 36.6 \\ 
		Europe (South West) & 603 &  &  &  &  &  & 7.7 & 12.2 & 10.7 & 11.2 & 11.2 & 7.5 & 9.5 & 5.3 & 10.1 & 11.2 & 7.3 \\ 
		\hline
		South America & 473 (+ 84) &  & 0.4 & 99.1 &  &  & 0.1 & 4.5 & 24.9 & 0.9 & 0.6 & 1.4 & 0.7 & 1.8 & 0.4 & 0.1 & 0.2 \\ 
		\hline
		Japan & 240 (+ 104) & 96.1 & 0.4 & 0.9 &  &  &  & 1.8 & 8.8 & 0.2 & 0.2 & 2.1 & 3 & 0.4 & 0.4 &  & 25.9 \\ 
		Asia (East) & 961 & 3.9 &  &  &  &  & 0.2 & 3.7 & 2.5 & 0.6 & 0.3 & 2.5 & 1.8 & 0.2 &  & 3 & 2.3 \\ 
		Philippines & 295 &  &  &  &  &  & 0.1 & 1.4 & 3.9 &  &  &  &  & 0.2 & 0.1 & 0.1 & 0.5 \\ 
		\hline
		Bangladesh & 223 (+ 86) &  &  &  &  &  & 0.6 &  & 1.2 & 1.1 & 0.8 & 2.8 & 2.8 & 0.9 &  &  & 1.4 \\ 
		Sri Lanka & 372 &  &  &  & 1.1 &  & 0.4 &  & 0.8 & 0.8 & 0.2 & 2.2 & 1.6 & 0.4 &  &  & 0.7 \\ 
		Pakistan & 400 &  &  &  &  &  & 0.8 &  &  & 0.4 &  & 6 & 2.5 & 0.7 &  &  &  \\ 
		\hline
	\end{tabular}
	\caption{Reference population with their size (N) and corresponding ancestry proportions in several GWAS datasets. Citations for the allele frequencies used: the Biobank Japan (BBJ, \cite{sakaue2021cross}), FinnGen (\url{https://r5.finngen.fi/}), GWAS in Peruvians \cite[]{asgari2020positively}, GWAS in Qataris \cite[]{thareja2021whole}, GWAS in Sub-Saharan Africans (Africa, \cite{chen2019genome}), the UK Biobank (UKBB, \cite{bycroft2018uk}), GERA \cite[]{hoffmann2018large}, PAGE \cite[]{wojcik2019genetic}, breast cancer (BrCa, \cite{michailidou2017association}), prostate cancer (PrCa, \cite{schumacher2018association}), coronary artery disease (CAD, \cite{nikpay2015comprehensive}), body fat percentage \cite[]{lu2016new}, COVID-19 \cite[]{ganna2021mapping}, eczema \cite[]{paternoster2015multi}, epilepsy \cite[]{consortium2018genome}, and serum urate \cite[]{tin2019target}. Several of them have been downloaded through the NHGRI-EBI GWAS Catalog \cite[]{macarthur2017new}. \label{tab:table1}}
\end{table}

>>>>

% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Wed Oct 27 13:40:20 2021
\begin{table}[htb]
	\centering
	\begin{tabular}{|l|c||c|c|c|c|c||c|c|c||c|c|c|c|c|c|c|c|}
		\hline
		Ancestry group & N & BBJ & FinnGen & Per\'u & Qatar & Africa & UKBB & GERA & PAGE & BrCa & PrCa & CAD & body fat & covid & eczema & epilepsy & urate \\ 
		\hline
		Africa (West) & 735 &  &  &  &  & 36.7 & 1.4 & 1.9 & 26.4 & 0.2 & 0.2 & 2.4 & 1 & 4 & 0.3 & 0.6 & 3.6 \\ 
		Africa (South) & 449 &  &  &  &  & 63.3 & 0.3 & 0.4 & 6.8 &  & 0.1 & 0.9 & 1.1 & 1.2 & 0.1 &  & 4 \\ 
		Africa (East) & 276 &  &  &  & 11.4 &  &  &  & 0.2 &  &  &  & 0.2 & 0.1 &  &  & 1.4 \\ 
		Africa (North) & 268 &  &  &  & 22.1 &  &  & 0.4 & 2 &  &  &  &  &  &  & 0.3 &  \\ 
		\hline
		Middle East & 523 &  &  &  & 63.5 &  & 1.3 & 3.4 & 0.5 & 2 & 2.2 & 5.2 & 2.9 & 1.5 & 1.6 & 3.2 & 2.8 \\ 
		\hline
		Ashkenazi & 1975 &  &  &  & 1.9 &  & 1.4 & 6 & 0.9 & 1.3 & 3.3 & 2.2 & 2.3 & 1.3 & 2 & 3.6 & 1.5 \\ 
		Europe (North East) & 320 &  & 8.9 &  &  &  & 3.8 & 7.7 & 0.7 & 9.6 & 10 & 10 & 11 & 11.7 & 10.1 & 8.9 & 7.5 \\ 
		Finland & 143 (+ 99) &  & 85.2 &  &  &  & 2.7 & 3.5 & 0.7 & 11.9 & 14.8 & 8.2 & 10.5 & 15.4 & 13.1 & 7.1 & 4.3 \\ 
		British-Irish Isles & 4000 &  & 5.1 &  &  &  & 79.1 & 53 & 8.9 & 59.8 & 56.1 & 46.6 & 49.2 & 54.8 & 61.7 & 62 & 36.6 \\ 
		Europe (South West) & 603 &  &  &  &  &  & 7.7 & 12.2 & 10.7 & 11.2 & 11.2 & 7.5 & 9.5 & 5.3 & 10.1 & 11.2 & 7.3 \\ 
		\hline
		South America & 473 (+ 84) &  & 0.4 & 99.1 &  &  & 0.1 & 4.5 & 24.9 & 0.9 & 0.6 & 1.4 & 0.7 & 1.8 & 0.4 & 0.1 & 0.2 \\ 
		\hline
		Japan & 240 (+ 104) & 96.1 & 0.4 & 0.9 &  &  &  & 1.8 & 8.8 & 0.2 & 0.2 & 2.1 & 3 & 0.4 & 0.4 &  & 25.9 \\ 
		Asia (East) & 961 & 3.9 &  &  &  &  & 0.2 & 3.7 & 2.5 & 0.6 & 0.3 & 2.5 & 1.8 & 0.2 &  & 3 & 2.3 \\ 
		Philippines & 295 &  &  &  &  &  & 0.1 & 1.4 & 3.9 &  &  &  &  & 0.2 & 0.1 & 0.1 & 0.5 \\ 
		\hline
		Bangladesh & 223 (+ 86) &  &  &  &  &  & 0.6 &  & 1.2 & 1.1 & 0.8 & 2.8 & 2.8 & 0.9 &  &  & 1.4 \\ 
		Sri Lanka & 372 &  &  &  & 1.1 &  & 0.4 &  & 0.8 & 0.8 & 0.2 & 2.2 & 1.6 & 0.4 &  &  & 0.7 \\ 
		Pakistan & 400 &  &  &  &  &  & 0.8 &  &  & 0.4 &  & 6 & 2.5 & 0.7 &  &  &  \\ 
		\hline
	\end{tabular}
	\caption{Reference population with their size (N) and corresponding ancestry proportions in several GWAS datasets. Citations for the allele frequencies used: the Biobank Japan (BBJ, \cite{sakaue2021cross}), FinnGen (\url{https://r5.finngen.fi/}), GWAS in Peruvians \cite[]{asgari2020positively}, GWAS in Qataris \cite[]{thareja2021whole}, GWAS in Sub-Saharan Africans (Africa, \cite{chen2019genome}), the UK Biobank (UKBB, \cite{bycroft2018uk}), GERA \cite[]{hoffmann2018large}, PAGE \cite[]{wojcik2019genetic}, breast cancer (BrCa, \cite{michailidou2017association}), prostate cancer (PrCa, \cite{schumacher2018association}), coronary artery disease (CAD, \cite{nikpay2015comprehensive}), body fat percentage \cite[]{lu2016new}, COVID-19 \cite[]{ganna2021mapping}, eczema \cite[]{paternoster2015multi}, epilepsy \cite[]{consortium2018genome}, and serum urate \cite[]{tin2019target}. Several of them have been downloaded through the NHGRI-EBI GWAS Catalog \cite[]{macarthur2017new}. \label{tab:table1}}
\end{table}
